\pdfoutput=1
\documentclass[10pt]{beamer}

%STANDARD PREAMBLE
%https://tex.stackexchange.com/questions/68821/is-it-possible-to-create-a-latex-preamble-header
\usepackage{../rsrc/beamer_preamble}

% RANDOM VARIABLE
\newcommand{\x}{X}
\newcommand{\y}{Y}

\title{Introductory Stuff}

\begin{document}

\maketitle

%\begin{frame}{Table of contents}
%  \setbeamertemplate{section in toc}[sections numbered]
%  \tableofcontents[hideallsubsections]
%\end{frame}

\begin{frame}{Course webpage}
\href{https://github.com/mikewojnowicz/stat_ml_anomaly/}{Click here for github repo}
\end{frame}

\begin{frame}{About your instructors}
\href{https://disc.tufts.edu/people}{Mike Wojnowicz and Karin Knudson}
\vfill
michael.wojnowicz@tufts.edu, karin.knudson@tufts.edu
\end{frame}
 
\begin{frame}{About you}

There are roughly 19 of us.  Let's take a minute to go around and do brief introductions (1 min each).  Making us all comfy with each other will help us to  have better discussions and hopefully work together better too.

\vfill

We would like each of you to say: 
\begin{itemize}
\item Your name
\item Your affiliation at Tufts
\item One hope that you have for this course.
\item One fear that you have for this course.
\item One hobby that you have.
\end{itemize}

\bf{Note:} Please treat these almost as 5 fill-in-the-blank sentences; we would like this part to be quickish, since we're still all one big group.   There will be time for more natural discussion as we go along (during the slide presentations and during group activities). 
\vfill

Karin and I will go first.
 
\end{frame}

\begin{frame}{On discussions}
During the slide presentations, please feel free to jump in \bf{at any time}.  We want this workshop to be interactive. 
\end{frame}


\begin{frame}{Other comments and remarks}

This is the first run of:
\begin{itemize}
 \item this workshop 
 \item  (for Mike) \it{any} virtual course. 
 \end{itemize}  

We are \it{very} open to feedback and tweaks as we go along.  Please send us a public chat, private chat, or e-mail at anytime with any suggestions or ideas.

\vfill
A few known open questions for now:
\begin{itemize}
\item How can we best set up the interactive activity component?
\item Should we set up a parallel Slack chat, so that the conversation can potentially be of higher quality?
\item Would it be easier to schedule breaks in advance, or take them in natural locations?
\end{itemize}


\end{frame}

\end{document}